Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-10-31 2016-Weak-FH-Bisim/WeakBisim.tex
Fig 1 et 2 + commentaires

The informal semantics of pNets is as follows. pLTSs behave more or less like  classical automata with conditional branching and variables. The actions on the \pLTS s can send or receive values, potentially modifying the value of variables. 
pNets are synchronisation entities: a pNet composes several subnets and  synchronisation vectors define how the subnets interact, where a subnet is either a pNet or a pLTS. Synchronisation between subnets is defined by synchronisation vectors that express how an action of a subnet can be synchronised with actions of other subnet, and how the resulting synchronised action is visible to the outside of the pNet. Synchronisation vectors also allow to explicitly export an action of a subnet to the next level, or to allow to subnets to synchronise and only exporting a non0observable action (provided such an non-visible action labels exist in the action algebra. Finally, a pNet can leave subnets undefined and instead declare holes with a well-defined signature. Holes can then be filled with a subnet. This is defined as follows.

@@

@@

\subsection{Running Example}
\TODO{Rabea: trouver reference !!}
To illustrate this work, we use a simple communication protocol, that provides safe transport of data between two processes, over unsafe media. The alternating bit protocol was first described in \cite{Bartlett:1969}.  Our specification  of the ABP is based on the one given in \cite{Vergamini:1986}.

Fig. \ref{SimpleProt:Spec} (left) shows the example principle: two unspecified
processes $P$ and $Q$ (Holes) communicate messages, with a data value
argument, through the two protocol entities $sender$ and
$receiver$. The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect some transport error, and signal it to the sender. The return $ack$ message from $receiver$ to $sender$ is supposed to be safe. The final transmission of the message to the recipient (Hole Q) include the value of the ``error counter'' $ec$.

This is only a graphical syntax,
with an obvious semantics for building the corresponding pNets.

Fig. \ref{SimpleProt:Spec} (right) shows the Schema of this system, and on the right side, its global specification, expressed as a pNet. 
The full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium. Fig. \ref{SimpleProt:Spec}, right, shows the pNet representing this global specification.

Fig. \ref{SimpleProt:Impl} show the pNet model of the protocol. When the medium detects an error (modeled by a local $\tau$ action), it sends back a $m\_error$ message to the $Sender$. The $Sender$ increments its error counter $c$, and resend the message (including $c$) to the medium, that will, eventually, transmit $m,c$ to the receiver.

@@

\begin{figure}[t]
   \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
   \includegraphics[width=6.5cm]{XFIG/SimpleProt-Spec}
   \caption{Specification pNet Schema and Specification}
   \label{SimpleProt:Spec}

@@

\begin{figure}[t]
  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt-pNet}}
  \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
\end{figure}

>>>>

The informal semantics of pNets is as follows. pLTSs behave more or less like  classical automata with conditional branching and variables. The actions on the \pLTS s can send or receive values, potentially modifying the value of variables. 
pNets are synchronisation entities: a pNet composes several subnets and  synchronisation vectors define how the subnets interact, where a subnet is either a pNet or a pLTS. Synchronisation between subnets is defined by synchronisation vectors that express how an action of a subnet can be synchronised with actions of other subnet, and how the resulting synchronised action is visible to the outside of the pNet. Synchronisation vectors also allow to explicitly export an action of a subnet to the next level, or to allow to subnets to synchronise and only exporting a non-observable action (provided such an non-visible action labels exist in the action algebra. Finally, a pNet can leave subnets undefined and instead declare holes with a well-defined signature. Holes can then be filled with a subnet. This is defined as follows.

@@

\subsection{Running Example}
To illustrate this work, we use a simple communication protocol, that provides safe transport of data between two processes, over unsafe media.

Fig. \ref{SimpleProt:Spec} (left) shows the example principle: two unspecified
processes $P$ and $Q$ (holes) communicate messages, with a data value
argument, through the two protocol entities. Process $P$ send an $p\_send(m)$ message to the $Sender$; this communication is denoted as $\underline{in(m)}$, where underline actions represent internal actions (similar to the $\tau$ of CCS), that cannot be further synchronised with the environment. At the other end process $Q$ receives the message from the $Receiver$. The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $p\_a$ and $q\_b$. The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect transport errors, and signal them to the sender. The return $ack$ message from $receiver$ to $sender$ is supposed to be safe. The final transmission of the message to the recipient (Hole Q) include the value of the ``error counter'' $ec$.

Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet of the system \emph{specification}:
the full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium. Fig. \ref{SimpleProt:Spec}, right, shows the pNet representing this global specification.

Fig. \ref{SimpleProt:Impl} show the pNet model of the protocol implementation. When the $Medium$ detects an error (modeled by a local $\tau$ action), it sends back a $m\_error$ message to the $Sender$. The $Sender$ increments its local error counter $c$, and resends the message (including $c$) to the $Medium$, that will, eventually, transmit $m,c$ to the $Receiver$.

@@

@@

\begin{figure}[t]
   \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
   \includegraphics[width=6.5cm]{XFIG/SimpleProt-Spec}
   \caption{Specification pNet Schema and Specification}
   \label{App:SimpleProt:Spec}

@@

\begin{figure}[t]
  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt-pNet}}
  \caption{Composed pNet with the Simple Protocol Implementation}  \label{App:SimpleProt:Impl}
\end{figure}
